%% Begin copyright
%%
%%  /home/jrf/Documents/books/Books20/Manuscript/books20.tex
%%  
%%   Part of the Books20 Project
%%
%%   Copyright 2008 James R. Fowler
%%
%%   All rights reserved. No part of this publication may be
%%   reproduced, stored in a retrival system, or transmitted
%%   in any form or by any means, electronic, mechanical,
%%   photocopying, recording, or otherwise, without prior written
%%   permission of the author.
%%
%%
%% End copyright

%
% The manuscript which may be of some importance
%
\documentclass{book}%

\usepackage{books20}
\addglobalbib{./../Docs/MasterBib.bib}

%
% History
% created 30 Nov 2008
%
%----------------------------------------------------------
\begin{document}

\title{\BookTitle}
\author{James R. Fowler}
\date{copy of \today}
\maketitle

\vspace*{5 in}
\ProjectCopyright{2008}

\tableofcontents

\chapter{Preface}
\import{./}{preface}

\chapter{Introduction}
\import{./}{intro}

\chapter{Astronomy before the Twentieth Century}
\import{./}{astro_pre}

\chapter{Astronomy and Astrophysics in the Twentieth Century}
\markboth{The Twentieth Century}{The Twentieth Century}
\import{./}{astro_20}

\chapter{The Process}
\import{./}{the_process}

\chapter{Speculations on the Future}

It is always perilous to speculate about the future.  What will be the
exciting topics in astronomy and astrophysics?  Will we see images of
exo-planets?  Will larger space telescopes give us views we can't
imagine today?

What of books in the age of the internet?  It is going to be
interesting to see how publishing changes in this age of information.
Will summary works still be printed? What of the permanence of
documents published on the web only?

\appendix

\chapter{The Books}
\import{./}{the_books}

\chapter*{Afterword}

The back matter often includes one or more of an index, an afterword,
acknowledgements, a bibliography, a colophon, or any other similar
item. In the back matter, chapters do not produce a chapter number,
but they are entered in the table of contents. If you are not using
anything in the back matter, you can delete the back matter \TeX\ command
and everything that follows it.

\printbibliography

%
% The End
%
\end{document}
