%% Begin copyright
%%
%%  /home/jrf/Documents/books/Books20/Manuscript/the_process.tex
%%  
%%   Part of the Books20 Project
%%
%%   Copyright 2008 James R. Fowler
%%
%%   All rights reserved. No part of this publication may be
%%   reproduced, stored in a retrival system, or transmitted
%%   in any form or by any means, electronic, mechanical,
%%   photocopying, recording, or otherwise, without prior written
%%   permission of the author.
%%
%%
%% End copyright

%%
%%   The chapter 'The Process' for
%%     the book "Some Important Books in Astronomy and
%%      Astrophysics in the 20th Century"
%%

\begin{itemize}
\item Chapter One: Introduction
  \begin{itemize}
  \item How were books used in Astronomy and Astrophysics when journal article
    were the main communications media?
  \item How does the use of books differ from that of the \Cen{19}?
  \item How does the use of books differ from other fields of art or science?
  \item What is an 'important' book? influence, topic matter, citations?
  \end{itemize}
  
\item Chapter Two: Astronomy before the \Cen{20}
  \begin{itemize}
  \item What was the state of Astronomy at the turn of the century?
  \item What were the important questions?
    \begin{itemize}
    \item Problems in Astronomy, Agnus Clerke, 1903, \cite{clerke:1903}
    \item Recent Advances in Astronomy, Alfred Frison, 1899 \cite{frison:1899}
    \item Norton History of Astronomy and Cosmology, 1995
    \item The General History of Astronomy, Cambridge Univ.\ Press
    \end{itemize}
  \end{itemize}
  
\item Chapter Three: Astronomy in the \Cen{20}
  \begin{itemize}
  \item What astronomical topics were important in the \Cen{20}?
    \begin{itemize}
    \item Source Book in Astronomy, 1900-1950, Harlow Shapely \cite{shapley:1960}
    \item A Source Book in Astronomy and Astrophysics, 1900-1975, Lang and Gingerich,
      \cite{lang:1978}.
    \item Norton History of Astronomy and Cosmology, 1995
    \item The General History of Astronomy, Cambridge Univ.\ Press
    \item IAU Commission for Documentation and Bibliography
    \end{itemize}	
  \end{itemize}
  
\item Chapter Four: The Process
  \begin{itemize}
  \item How do I locate books published in the century?
    \begin{itemize}
    \item Kemp 1970
    \item DeVorkin 1982
    \end{itemize}
  \item How do I identify the important ones? Ask astronomers; read biographies; check
    correspondence.
  \end{itemize}
  
\item Chapter Five: Speculations on the Future
  \begin{itemize}
  \item What are the important questions at the end of the \Cen{20}?
  \item Where will books go from here with the advent of the web?
  \end{itemize}
  
\end{itemize}
