%% Begin copyright
%%
%%  /home/jrf/Documents/books/Books20/Docs/Style/style_latex.tex
%%  
%%   Part of the Books20 Project
%%
%%   Copyright 2018 James R. Fowler
%%
%%   All rights reserved. No part of this publication may be
%%   reproduced, stored in a retrival system, or transmitted
%%   in any form or by any means, electronic, mechanical,
%%   photocopying, recording, or otherwise, without prior written
%%   permission of the author.
%%
%%
%% End copyright

%%
%%  The style that I will use for LaTeX 2e documents 
%%
\section{General Comments}

Documents for the \ProjectTitle\ project should be written in
\LaTeXe. Most documents will be articles but the manuscript (and this
style guide) should be in the book document class. The reasoning
behind using \LaTeXe\ is that I expect academic publishers to prefer
or at least have available a \LaTeXe\ class package.  It will be
difficult if I need to convert these documents to Microsoft
Word\texttrademark\ or some other formatting package.

A good, general purpose on-line reference for \LaTeXe\ can be found at
the Share \LaTeX\ web site,
\href{http://www.sharelatex.com/learn}{www.sharelatex.com/learn}.
More detailed information can be found at The Comprehensive
\TeX\ Archive Network, \href{ctan.org}{ctan.org}

\subsection{Font Conventions}

Italics is used for book titles and is obtained with the command
\verb|\textit{}| or with the command\verb|\bt{}|.

Typewriter for computer commands and files and is obtained with the
command \verb|\texttt{}|

Bold is used for the project name and is obtained with the command
\verb|\textbf{}|

\section{Document Design with \texttt{books20.sty}}

The \texttt{books20.sty} style package was written to support
\ProjectTitle\ documents and shall be used in all project
\LaTeXe\ documents. To include it in your document add
\verb|\usepackage{books20}| in the preamble of the file, there are no
options to the style file at this time. Note that \texttt{books20.sty}
is designed for \LaTeXe\ and may not work with \LaTeX\ 2.09.

The package imports the following additional packages so you
do not need to explicitly add the to your \LaTeXe\ documents.

\begin{itemize}
\item inputenc \cite{Jeffrey2018} (with the utf8 option)
\item hyperref \cite{Rahtz2017}
\item longtable \cite{Carlisle2014}
\item import \cite{Arseneau2009}
\item biblatex \cite{Lehman2018} (with biber backend option and the
  master bibliography file \texttt{./Books20/Docs/MasterBib.bib})
\end{itemize}


\begin{itemize}
\item The \texttt{import} package allows you to place sections in a
  separate file and use the \verb|\import{}{}| command in the document
  to include the file within the document. The first argument is the
  directory path, the second argument is the file name. As an example,
  use \verb|\import{./}{style_latex}|.  By using the \texttt{import}
  package it is possible to use the same file in different documents
  without having to clean up the file. The \verb|\subimport{}{}|
  command has the same calling syntax but the file locations are
  relative to the first \verb|\import|. It is possible to nest
  \verb|\import| commands whereas it is not possible to nest
  \verb|\include| commands. This feature shall be used inLaTeX2e\
  documents to allow greater flexibility for reuse. The imported
  files may have \verb|\section| commands but should not have
  \verb|\chapter| commands.

\item {The input encoding package \texttt{inputenc} shall be used
  so that UTF-8 character encoding can be utilized. Note that this
  package is included automatically with in the \texttt{books20} package.

  Then a sentence might be written as
  
  \verb| Das astronomische Weltbild gemäß jüngster Forshung|
  to produce

  Das astronomische Weltbild gemäß jüngster Forshung.

  But you can still use the standard \LaTeX\ encoding
  
  \verb| Das astronomische Weltbild gem\"{a}{\ss} j\"{u}ngster Forshung|
  to produce the same thing, e.g.

  Das astronomische Weltbild gem\"{a}{\ss} j\"{u}ngster Forshung.

  This will be useful when creating \LaTeXe\ files from the database
  which is in UTF-8 encoding.
}

\item In Emacs we can produce UTF-8 characters with C-x 8 mark letter.
  For example, to produce ö use the key strokes C-x 8 \verb|"| o. Use
  C-x 8 C-h to get a list of character encoding.
  
\item May wish to consider the use of the \texttt{subfiles} or
  \texttt{standalone} packages if the number of files gets
  large. These packages allow you to precompile files and avoid long
  compiles, simlar to the \texttt{make} command in Unix.  However,
  these packages may conflict with the \texttt{import} package.


\end{itemize}

\subsection{Defined Commands}

\begin{itemize}

\item \verb|\Cen{19}| is used to produce century names,
  e.g.\ \Cen{19}. Note that it works only for the \Cen{1} through the
  \Cen{30}. Other centuries that would use the superscript
  \textsuperscript{th} are supported but not ones that want to use the
  superscripts \textsuperscript{st} or \textsuperscript{nd}.
  Should this command be rewritten to use \verb|\textsuperscript{}|

\item Other superscripts may be written with the command
  \verb|\Ord{}{}|.  For example, you may write \verb|\Ord{42}{nd}| to
  produce \Ord{42}{nd}.

\item \verb|\bt{Book Title}| produces book titles in italic face,
e.g.\ \bt{Book Title} is the title of a book.

\item \verb|\ProjectTitle\ | produces the project title in bold face,
  e.g.\ the \ProjectTitle\ project is the name of this project.

\item \verb|\BookTitle\ | produces the book title in italic face,
  e.g.\ \BookTitle\ or whatever I (or my editor) choose for a title.

\end{itemize}

\section{Still to Do}

\begin{itemize}

\item How to handle internal and external references.  Written
  documents will be used both as paper documents and as on-line
  eDocuments and the full link should be available in either
  case. External references should be handled in the bibliography
  package. Internal references, both URLs and links to pages in the
  document, need to be researched.  As an example,
  there is a need for mutual references between this chapter and the
  chapter on English Grammer and Style. Question, should we use
  the bibliography for external URLs (web sites) or should the
  be placed in a footnote?  The choice may depend on the specific
  context of the document.

\item Work out other font formats as required. For example, an included
  file or package should be in teletype format using \verb|\texttt{}|.
  Although there will not be much call for such in the manuscript. Also
  consider the use of the NFSS font selection system within \LaTeXe.

\end{itemize}

\section{An Example Document}

Here is an example document so you can see what the \LaTeX\ commands are.

\begin{verbatim}

%%
%%
%% style_guide.tex
%%
%%   The style that I will used for 
%%   the book project "Some Important Books in Astronomy
%%    and Astrophysics in the 20th Century"
%%
%%   Copyright 2017 James R. Fowler
%%
%%   All rights reserved. No part of this publication may be
%%   reproduced, stored in a retrival system, or transmitted
%%   in any form or by any means, electronic, mechanical,
%%   photocopying, recording, or otherwise, without prior written
%%   permission of the author.
%%
%%
%%
\documentclass{book}

\usepackage{books20}
\addglobalbib{./../../Docs/MasterBib.bib}
\addbibresource{localbib.bib}

\begin{document}
\title{Style Guide for the \ProjectTitle\ Project}
\author{James R. Fowler}
\date{2017-12-15}

\maketitle
\tableofcontents
\listoftables 

\Chapter{\LaTeX2e\ Documents}
\import{./}{sytle_latex}

\chapter{Python Programming}
\import{./}{style_python}
\end{document}

\end{verbatim}

The following would be imported from  the style\_latex.tex document.

\begin{verbatim}

\section{General Comments}

The first of many sections for the book \BookTitle.  You
can cite Basbanes' \cite{Basbanes2003} book on libraries
like this.

\section{Using UTF-8}

You can use UTF-8 characters by using the
 \verb|usepackage[utf-8]{inputenc}| package.

Then a sentence might be written as

\verb|Das astronomische Weltbild gemäß jüngster Forshung|
to produce

Das astronomische Weltbild gemäß jüngster Forshung.

But you can still use the standard \LaTeX\ encodings

\verb|Das astronomische Weltbild gem\"{a}{\ss j\'{u}ngster
       Forshung| to produce the same thing, e.g.

Das astronomische Weltbild gem\"{a}{\ss} j\'{u}ngster Forshung.

\subsection{Long Tables}

You can make a table in longtable format.

\begin{longtable}[p]{l l l}
  \caption{\bfseries Harvard Observatory Monographs} \\
  \label{HMA:1} \\

  Title & Author(s) & Date \\
  \hline\hline
  \endfirsthead

  \multicolumn{3}{c}{Continuation of Harvard Obs.\ Monographs} \\
  Title & Author(s) & Date \\
  \hline\hline
  \endhead

  \hline
  \endfoot
  
  \hline\hline
  \endlastfoot

  1 \bt{Stellar Atmospheres} & Cecilia Payne & 1925 \\

  2 \bt{Star Clusters} & Harlow Shapley & 1930 \\

  3 \bt{The Stars of High Luminosity} & Cecilia Payne & 1930 \\

  
\end{longtable}

\printbibliography

%% End style_latex.tex
\end{verbatim}

