%% Begin copyright
%%
%%  /home/jrf/Documents/books/Books20/Docs/Hjs/bibliography.tex
%%
%%   Part of the Books20 Project
%%
%%   Copyright 2022 James R. Fowler
%%
%%   All rights reserved. No part of this publication may be
%%   reproduced, stored in a retrival system, or transmitted
%%   in any form or by any means, electronic, mechanical,
%%   photocopying, recording, or otherwise, without prior written
%%   permission of the author.
%%
%%
%% End copyright

Harlan James Smith (1924--1991) was born in Wheeling, West Virginia on
25 August 1924, graduating high school there in 1942\footnote{Much of
this information has been taken from the obituary written by James
N.~Douglas in the Bulletin of the AAS (\cite{Douglas1992Harlan}) as
well as from the pamphlet ``The Harlan J.~Smith Centennial
Professorship in Astronomy'' (see entry \myhref{3} in the
catalogue.) and the pamphlet ``The Edward Randall Jr.,M.D.~Centennial
Professorship in Astronomy'' (see entry \myhref{5} in the
catalogue).}. Joining the Army Air Corp in 1943, he finished his
service career as a meteorologist on Guadalcanal in 1946.  Harlan
obtained his undergraduate degree in 1949 and his Ph.D in 1955, both
from Harvard. His thesis focused on short period variable stars where he
recognized that they were more like Cepheids than RR Lyrae stars.
These stars he called dwarf Cepheids though they are now called delta
Scuti stars (\cite{HJS1955}, \cite{HJSPhD}),

Harlan joined the faculty at Yale in 1953, ultimately obtaining the rank of
Associate Professor. There he began working in radio astronomy where
he and his students studied the decameter radio pulses from
Jupiter. He and Dorrit Hoffleit also studied the optical variability of
the newly discovered quasars and found unequivocal evidence for
variations in 3C273 implying a small physical size
(\cite{HJS1963}).

In 1950, while in graduate school at Harvard, Harlan met Joan Greene
who was attending Radcliffe College. There were married in December
1950 and had four children, Nat, Julie, Tad, and Hannah.

In 1963 Harlan was recruited to be the first ``Texas'' director of the
McDonald Observatory as well as Chairman of the Astronomy Department
at the University of Texas at Austin. During his directorship the
observatory and the department grew in size in both the staff and the
faculty with a strong emphasis on undergraduate teaching in the
department. He resigned as Department Chairman in 1978 citing the
heavy work load from the enlarged staff but remained as Director of
McDonald Observatory. He was appointed to the Edward Randell Jr.,MD
Centennial Professorship in Astronomy in 1984 (see catalogue
entry \myhref{5}).  Harlan was also committed to public education and
outreach.  He encouraged the publication of the McDonald Observatory
News (later Star Date magazine) and the construction of the Moody
Visitor's Center.

A large observatory needed to have the best telescopes and
instrumentation so the 82-inch telescope was refurbished in the
mid-1960's and talks for a larger telescope began.  The
107-inch telescope was dedicated in 1969 and was later renamed the
Harlan J.~Smith Telescope in 1995. Lunar laser ranging signals from
the moon were first detected at McDonald in Aug 1969 and lunar
ranging continued at the 107-inch until 1985. The project was
continued on a series of smaller telescopes until September 2020; one
of the longest experiments at the McDonald Observatory. The
construction of the 107-inch telescope required support for the
visiting astronomers as well as the larger staff so the Transient
Quarters (later the Astronomer's Lodge) was built as well as 15
additional staff houses. A program in radio astronomy was developed
with the construction of the University of Texas Radio Observatory
(UTRAO) in Marfa, Texas. The Millimeter Wave Observatory was later
moved from campus to the observatory. In 1978 he started advocating
for an even larger telescope at McDonald, the 300-inch Eye of Texas
(see entry \myhref{396} and \myhref{417} of the catalogue). This was
not to be due to the collapse of the Texas oil economy in 1985. He
did, however, start discussions with Penn State University about the
433-inch Hobby-Eberly Telescope (the former Spectroscopic Survey
Telescope, see entry \myhref{4} of the catalogue) which was dedicated
in 1997,

Harlan was strongly committed to public service for astronomy and was
a member of the Royal Astronomical Society, the International
Astronomical Union, the American Association for the Advancement of
Science, and the American Astronomical Society (AAS). He was Chairman
of the Planetary Division of the AAS from 1974--1976, AAS Council
Member from 1975--1978, and Vice-President of the AAS from
1977-1979. He served on the national stage as a member of the
Committee on the Large Space Telescope (later the Hubble Space
Telescope) from 1966--1970 and a member of the Space Science Board
(SSB) of the National Academy of Sciences where he was also Chairman
of the Committee on Space Astronomy and Astrophysics of the
SSB. Harlan was a member of the Board of Directors of the Associated
Universities for Research in Astronomy (AURA), 1972--1983, and was
Chairman of the Board from 1980--1983. He was Chairman of the
Management/Operations Working Group for Planetary Astronomy (NASA)
from 1988--1991.  He received the NASA Distinguished Public Service
Medal in 1991 (see entry \myhref{507} of the catalogue).

Harlan retired as Director of the McDonald Observatory in 1989 but
continued to teach at the university and engage in public service work
until his death on 17 October 1991.


