\section{Sky \& Telescope}

These note are taken from \bt{Sky \& Telescope}, volume 1, number 1,
November 1941.

\bt{Sky \& Telescope} began in Nov, 1941, as a merger between \bt{The
  Sky} and \bt{The Telescope}, both of which were losing money at the
time.  The first editor was Charles A.~Federer jr.\ and his wife Helen
Spencer Federer. The list of issues can be found in Table \ref{skytel:1}.

\bt{The Telescope} was published starting in 1931 at
the Perkins Observatory of the Ohio Wesleyan University and was edited
by Harlan T.~Stetson. Three years later he moved to the Massachusetts
Institute of Technology where he invited the Bond Astronomical Club and
the Harvard Observatory to take over the magazine. Thus in June, 1934
Dr.~Loring B.~Andrews became the editor and publication began in Cambridge,
Massachusetts.  When Andrews left for England in 1937, Donald H.~Menzel
became the editor.

\bt{Amateur Astronomer} was first published in April, 1929, by the
Amateur Astronomical Association, which was headquartered in the American
Museum of Natural History in New York, as a 4 page monthly bulletin of
short articles and items of interest for the coming month.  With
Volume IV, Winter 1933/34 the magazine took the step to a larger
quarterly format.  In October of 1936 it merged with the \bt{Monthly
  Bulletin} of the Hayden Planetarium and the name was changed to
\bt{The Sky}. By 1939 the American Museum could no longer financially
support the magazine and it passed into the hands of assistant
editor Charles and Helen Federer. \bt{The Sky} continued through
its fifth volume and then merged to become \bt{Sky \& Telescope}.

My collection of \bt{Sky \& Telescope} was received from Dr. John
Kormendy at the University of Texas/Austin. He started his collection
in Dec 1965 and continued it until I received it in 30 Jan 2016.  The
collection is essentially complete though there are some missing
issues as indicated in the table \ref{skytel:1}. There were also some
earlier issues that John had including Volume 1, number 1, Nov 1941.
The collection also contained Volume 1 number 7, Volume 8 number 11
and number 12, and Volume 17 May 1958 and number 11 Sept 1958.  The
magazine started in Nov 1941 so that issue was numbered as volume 1,
issue 1 while volume 1 issue 12 was Oct 1942.  The numbering scheme
continued in this fashion until volume 19 in 1960 when the number was
changed to start in January and the publication was issued in two
volumes per year; the first volume contained January to June and the
second volume contained July to December. Each volume contained number
1 through 6.  Volume 18 then had only two issues for November and
December respectively.  VERIFY THIS LAST STATEMENT!

A couple of interesting typographical error are eveident. The July
1982 issue which should have been volume 64 number 1 but instead the
masthead shows volume 63 number 7. There was no volume number on the
front cover at that time. In addition volume 113 number 2, Feb 2007,
is labeled Nov 2006 on the front cover. However the spine and the
masthead show the correct month and year.
