%% Begin copyright
%%
%%  /home/jrf/Documents/books/Books20/Docs/Series/cambridge.tex
%%
%%   Part of the Books20 Project
%%
%%   Copyright 2020 James R. Fowler
%%
%%   All rights reserved. No part of this publication may be
%%   reproduced, stored in a retrival system, or transmitted
%%   in any form or by any means, electronic, mechanical,
%%   photocopying, recording, or otherwise, without prior written
%%   permission of the author.
%%
%%
%% End copyright
\section{Cambridge University Press}

\subsection{Cambridge Astrophysics Series}

The {\bfseries Cambridge Astrophysics Series} was started in 1978 and
consists of high-quality books targeted for astronomers and graduate
students. The series publishes monographs, reviews, and textbooks in
all areas of astophysics. The general editors of the series as of 2020
are Andrew King, Douglas Lin, Stephen Maran, Jim Pringle, Martin Ward,
and Robert Kenicutt.  The web site can be found at
\url{https://www.cambridge.org/us/academic/subjects/physics/series/cambridge-astrophysics}
(last accessed 2020-03-02-06).  A list of the books in the series can
be found in table \ref{caps:1}.  Still need to get publishing
information and items later than 1990.

\subsection{Cambridge Planetary Science}

This series publishes reference works and postgraduate level textbooks
on terrestrial and gas giant plants with their satellites, asteriod,
comets, meteorites, Solar System evolution, the interplanetary medium,
and extra-solar planets.  The general editors as of 2020 are Jim Bell,
Leigh Fletcher, David Jewitt, Ralph Lorenz, Francis Nimmo, and David
Vokrouhlický.  The general web site is
\url{https://www.cambridge.org/us/academic/subjects/physics/computational-science-and-modelling/series/cambridge-planetary-science}
(last accessed 2020-02-06).
