%%
%%
%% handbuch.tex
%%
%%   Notes on reference works, hand books, and compendia 
%%   in astronomy and astrophysics  This is information used
%%   with the book project "Some Important Books in Astronomy
%%    and Astrophysics in the 20th Century"
%%
%%   Copyright 2017 James R. Fowler
%%
%%   All rights reserved. No part of this publication may be
%%   reproduced, stored in a retrival system, or transmitted
%%   in any form or by any means, electronic, mechanical,
%%   photocopying, recording, or otherwise, without prior written
%%   permission of the author.
%%
%%
%%
\documentclass{article}

\usepackage{books20}

\begin{document}

%% Front matter
\title{Handbooks and Reference Works in Astronomy and Astrophysics}
\author{James R. Fowler}
\date{copy of \today}

\maketitle

% \tableofcontents
% \listoftables

\section{Introduction}

How did we google before Google\texttrademark? How did we yahoo before Yahoo\texttrademark? And for
the old timers, how did we alta vista before Alta Vista\texttrademark?

Some profound and relevant statements about handbooks, compendia, and reference
works in \Cen{20} astronomy and astrophysics.

\section{Other Works}

\begin{itemize}
\item \bt{Handw\"{o}rterbuch der Astronomie und Mitwirkung}, Hand Dictionary of Astronomy, edited by Karl Wilhelm Valentiner (1845--1931)

\item \bt{Handbuch der Astrophysik}, editors G.\ Eberhard, A.\ Kohlsch\"{u}tter, and H. Ludendorff, J. Springer, pale orange cloth with gold stamped front cover and spine. McD has a copy.
  \begin{itemize}
  \item Volume 1, 1933, Grundlagen der Astrophysik,
  \item Volume 2, Grundlagen der Astrophysik
    \begin{itemize}
    \item 1\textsuperscript{st} Half, 1929
    \item 2\textsuperscript{nd} Half, 1931, AJB 33.35.91
    \end{itemize}
  \item Volume 3
    \begin{itemize}
    \item 1\textsuperscript{st} Half, 1930
    \item 2\textsuperscript{nd} Half, 1930
    \end{itemize}
  \item Volume 4, 1929,  Das Sonnesystem
  \item Volume 5, Der Sternsystem
    \begin{itemize}
    \item 1\textsuperscript{st} Half, 1932, AJB 34.35.01
    \item 2\textsuperscript{nd} Half, 1933
    \end{itemize}
  \item Volume 6, 1928, Das Sternsystem
  \item Volume 7, 1936 Erg\"{a}nzungsband, Supplement --- Ber\"{u}ckschtigend die Literatur bis ende 1934 nebst einem general register des gesamtwerkes
  \end{itemize}

\item \bt{Handbuch der Physik}, Encyclopedia of Physics, editor S.\ Fl\"{u}gge, Springer-Verlag
  \begin{itemize}
  \item Volume 50 1958 Astrophysics I Stellar Surfaces? Binaries
  \item Volume 51 1958 Astrophysics II Stellar Structure
  \item Volume 52 1959 Astrophysics III The Solar System. HJS Library has this volume in a dust jacket/
  \item Volume 53 1959 Astrophysics IV Stellar Systems
  \item Volume 54 1962 Astrophyisics V Miscellaneous
  \end{itemize}

\item \bt{Landolt-B\"{o}rnstein New Series}
  
\item \bt{Astrophysics Quantities}, edited by C.\ W.\ Allan. At least 4 editions. Mentioned in Tom Wolfe's \bt{The Right Stuff} (Get reference).
  \begin{itemize}
  \item 1\textsuperscript{st} edition ??? ???
  \item 2\textsuperscript{nd} edition 1963 Athlone Press
  \item 3\textsuperscript{rd} edition 1973 Athlone Press
  \item 4\textsuperscript{th} edition 2000 The AIP Pres
  \end{itemize}

\item \bt{Basic Astronomical Data}, 1963, editor K.\ AA.\ Strand

\item \bt{Astronomy Data Book}, 1972, editors J.\ Hedley Robinson and James Muirden, Halsted Press, a divsion of John Wiley and Sons, 2\textsuperscript{nd} edition 1979

\item \bt{Astrophysical Formulae}, 1974, Kenneth R.\ Lang, Springer-Verlag, 2\textsuperscript{nd} edition 1980

\item \bt{Handbook of Space Astronomy \& Astrophysics}, 1982, edited by Martin V.\ Zombeck, Cambridge University Press, 2\textsuperscript{nd} edition 1990
  
\end{itemize}

\end{document}

