%% Begin copyright
%%
%%  /home/jrf/Documents/books/Books20/Docs/Series/HarvardBooksAstronomy.tex
%%  
%%   Part of the Books20 Project
%%
%%   Copyright 2017 James R. Fowler
%%
%%   All rights reserved. No part of this publication may be
%%   reproduced, stored in a retrival system, or transmitted
%%   in any form or by any means, electronic, mechanical,
%%   photocopying, recording, or otherwise, without prior written
%%   permission of the author.
%%
%%
%% End copyright

%%
%%   Notes on the books in the series Harvard Books on Astronomy
%%   from the Harvard University Press.  This is information used
%%   with the book project "Some Important Books in Astronomy
%%    and Astrophysics in the 20th Century"
%%
\section{Harvard University Press}

This information comes in part from the web pages of Rudi
Lindner\footnotemark at the University of Michagan, Ann Arbor. They
appear to have been written during 2001 and were presented at the
January 2002 AAS meeting.

\footnotetext{\url{http://www-personal.umich.edu/~rpl/HarvardBooksOnAstronomy.htm} last accessed 2017-12-15.}

\subsection{Harvard Books on Astronomy}
\subsubsection{Series One}

Edited by Harlow Shapley and Bart J.\ Bok and published by The
Blakiston Company of Philadephia, Pennsylvania between 1941 and 1951.
This was a collection of popular books on astronomical topics with the
latest science presented by acknowledged experts in the field. See
table \ref{HBA:1} for a list of publications.

\begin{longtable}[p]{l l l}
  \caption{\bfseries Harvard Books on Astronomy Series One} \\
  \label{HBA:1} \\
  
  Title & Author(s) & Date \\
  \hline\hline
  \endfirsthead

  \multicolumn{3}{c}{Continuation of Series One} \\
  Title & Author(s) & Date \\
  \hline\hline
  \endhead

  \hline
  \endfoot
  
  \hline\hline
  \endlastfoot

  
  \bt{Earth, Moon, and Planets} & Fred L.\ Whipple & 1st ed. Feb 1941 \\
  & & second printing 1944 \\
  & & third printing 1945 \\
  & & fourth printing 1946 \\
  & & fifth printing 1947 \\

  \bt{Between the Planets} & Fletcher G.\ Watson & 1st ed. 1941 \\
  & & second printing 1945 \\

  \bt{The Milky Way} & Bart J.\ Bok & 1st ed. 1941 \\
  &  Priscilla F.\ Bok & 2nd revised ed. 1945 \\
  & & second printing Oct 1946 * \\

  \bt{Atoms, Stars and Nebulae} & Leo Goldberg & 1st ed. 1941 \\
  &  Lawrence H.\ Aller & second printing Feb1944 * \\
  & & third printing Apr 1945 * \\
  & & fourth printing Sept 1946 * \\
  & & fifth printing 1950 \\

  \bt{The Story of Variable Stars} & Leon Campbell & 1st ed. Oct 1941 \\
  &  Luigi Jacchia & second printing Feb 1945 \\
  & & third printing Jan 1946 \\
  & & w/additions \\

  \bt{Galaxies} & Harlow Shapley & 1st ed. 1943\footnotemark \\
  & & second printing Oct 1944 * \\
  & & third printing 1945 \\
  & & fourth printing 1947 \\

  \bt{Telescopes and Accessories} & George Z.\ Dimitroff & 1st ed. Feb 1945 * \\
  & James G.\ Baker & second printing Dec 1945 \\
  & & third printing 1948 \\

  \bt{Our Sun} & Donald H.\ Menzel & 1st ed. 1949 \\
  & & second printing 1950 \\

  \bt{Inside the Stars} & Theodore E.\ Sterne & never published \\
  & Martin Schwarzchild & \\

  \bt{The Relativistic Universe} & Philipp Frank & never published \\

\end{longtable}

\footnotetext{Shapley's annotated copy of \bt{Galaxies} series one at ABE,
  \$7,995. Last accessed 2018-07-28.
  \url{https://www.abebooks.com/servlet/BookDetailsPL?bi=16312048563&searchurl=tn\%3DGalaxies\%26sortby\%3D1\%26an\%3DShapley&cm\_sp=snippet-\_-srp1-\_-title1}}

\subsubsection{Series Two}

The Harvard University Press took over publication of the series in
1952 when the Blakiston Company, following its acquisition by
Doubleday Doran in 1951, ceased to publish works on astronomy. New
titles were added and new editions of some of the previous volumes
appeared.  The series editors were now Harlow Shapely and Cecilia
Payne-Gaposchkin. See table \ref{HBA:2} for the publication history of
this series

\begin{longtable}[p]{l l l}
  \caption{\bfseries Harvard Books on Astronomy Series Two} \\
  \label{HBA:2} \\

  Title & Author(s) & Date \\
  \hline\hline
  \endfirsthead

  \multicolumn{3}{c}{Continuation of Series Two} \\
  Title & Author(s) & Date \\
  \hline\hline
  \endhead

  \hline
  \endfoot
  
  \hline\hline
  \endlastfoot

  \bt{Earth, Moon and Planets} & Fred L.\ Whipple & 1st ed. 1952 \\
  & & 2nd ed. 1963 \\
  & & 3rd ed. 1968 \\
  & & second printing unk \\
  & & third printing 1970 \\
  & & fourth printing unk \\
  & & fifth printing 1976 \\
  & & sixth printing 1978 \\
  retitled \bt{Orbiting the Sun} & & new ed.  1981 \\

  \bt{Stars in the Making} & Cecilia Payne-Gaposchkin & 1st ed. Nov 1952 \\
  
  \bt{Between the Planets} & Fletcher G.\ Watson & 2nd ed. 1956 \\
  
  \bt{The Milky Way} & Bart J.\ Bok & 3rd ed. 1957 \\
  & Priscilla F.\ Bok & second printing 1968 * \\
  & & 4th ed. 1974 \\
  & & 5th ed. 1981 \\
  
  \bt{Our Sun} & Donald H.\ Menzel & 2nd ed. 1959 \\
  
  \bt{Galaxies} & Harlow Shapely & 2nd ed. 1961 \\
  & revised by Paul W.\ Hodge & 3rd ed. 1972 \\
  
  \bt{Tools of the Astronomer} & Gerhard R.\ Miczaika & 1st ed. 1961 \\
  & William M.\ Sinton & \\
  
  \bt{Atoms, Stars and Nebulae} & Lawrence H.\ Aller & 2nd ed. 1971 \\
  & & second printing 1975 \\
  & & 3rd ed. 1991 \\
  
  \bt{Stars and Clusters} & Cecilia Payne-Gaposchkin & 1st ed. 1979 \\
\end{longtable}


\subsection{Harvard Monographs in Astronomy}

Published by the Harvard University Press for the Harvard Observatory.
These books were professional monographs designed for the working
astronomer. The monograph publication format was chosen for those
works which would require more space than an article or but that were not
simply tables of data which were published as part of the
Harvard's Annals series. Thus there was no general editor. Although
published over many years these volumes recognize some of the
milestones in Astronomy and Astrophysics.  The only dust jacket I have
is on my copy of volume 6.  I don't know if the other volumes were
issued with dust jackets as I see few copies on the market for these
works.  See table \ref{HMA:1} for the publishing details.

\begin{longtable}[p]{l l l}
  \caption{\bfseries Harvard Observatory Monographs} \\
  \label{HMA:1} \\

  Title & Author(s) & Date \\
  \hline\hline
  \endfirsthead

  \multicolumn{3}{c}{Continuation of Harvard Obs.\ Monographs} \\
  Title & Author(s) & Date \\
  \hline\hline
  \endhead

  \hline
  \endfoot
  
  \hline\hline
  \endlastfoot

  1 \bt{Stellar Atmospheres} & Cecilia Payne & 1925 * \\

  2 \bt{Star Clusters} & Harlow Shapley & 1930 * \\

  3 \bt{The Stars of High Luminosity} & Cecilia Payne & 1930 * \\

  4 \bt{The History and Work} & Solon L.\ Bailey & 1931 \\
  \bt{\ \ \ \  of the Harvard Observatory} & & \\

  5 \bt{Variable Stars} & Cecila Payne-Gaposchkin & 1938 * \\
  & Sergei Gaposchkin & \\

  6 \bt{An Introduction to the} & Zden\v{e}k Kopal & 1946 * \\
  \bt{\ \ \ \ Study of Eclipsing Variables} & & \\

  7 \bt{Centennial Symposia} & & 1948 \\
  
\end{longtable}
