%% Begin copyright
%%
%%  /home/jrf/Documents/books/Books20/Docs/Series/interscience.tex
%%
%%   Part of the Books20 Project
%%
%%   Copyright 2020 James R. Fowler
%%
%%   All rights reserved. No part of this publication may be
%%   reproduced, stored in a retrival system, or transmitted
%%   in any form or by any means, electronic, mechanical,
%%   photocopying, recording, or otherwise, without prior written
%%   permission of the author.
%%
%%
%% End copyright

%%
%% Notes on the books in the series Interscience Tracts on
%%  Physics and Astronomy from Interscience Publishers, a division
%%  of John Wiley & Sons.  This is information used
%%  with the book project "Some Important Books in Astronomy
%%  and Astrophysics in the 20th Century"
%%
\section{John Wiley \& Sons}

The published company John Wiley \& Sons was founded in 1807 in
Manhatten. A number of histories of the company have been published.
The first in 1957 entitled \bt{The First One Hundred and Fifty Years: A
  History of John Wiley and Sons Incoroprated} with a second history in
1982 entitled \bt{Wiley: One Hundred and Seventy Five Years of
  Publishing}.  A number of independent histories have also been
published.  See the Wikepedia article on the company for references,
\url{https://en.wikipedia.org/wiki/Wiley_(publisher)}.

\subsection{Interscience Tracts on Physics and Astronomy}

The series \textbf{Interscience Tracts on Physics and Astronomy} began
in 1954. The first editor was R.~E. Marshack, of the University of
Rochester. The series was originally published by Interscience
Publishers. The company was purchased by John Wiley \& Sons in 1961
who continued the series through at least 1968. I have not found
volumes after this date although there are vendors on ABE that list a
volume published in 1972.  However, the cover does not state that it
is a part of this series.  This was one of a number of series
published by Interscience Publishers. They also published works on
astronomy that are not part of this series.

