%% Begin copyright
%%
%%  /home/jrf/Documents/books/Books20/Docs/Series/series.tex
%%  
%%   Part of the Books20 Project
%%
%%   Copyright 2017 James R. Fowler
%%
%%   All rights reserved. No part of this publication may be
%%   reproduced, stored in a retrival system, or transmitted
%%   in any form or by any means, electronic, mechanical,
%%   photocopying, recording, or otherwise, without prior written
%%   permission of the author.
%%
%%
%% End copyright

%%
%%   Notes on the books and articles that have been part of a series
%%   from a publisher.  This is information used
%%   with the book project "Some Important Books in Astronomy
%%    and Astrophysics in the 20th Century"
%%
\documentclass[letterpaper]{article}

\usepackage{books20}

% need to set text width to soak up space
% otherwise is is soaked up in the right hand margin
% \paperwidth is 614.295pt (8.5in)
% \textwidth = 345.0pt
% \hoffset = 0
% \oddsidemargin = 62pt
% left/right margin is 72.27pt (1in) + \hoffset + \oddsidemargin
%
% so \paperwidth = 2 * (72.27 + \oddsidemargin) + \textwidth
% or \textwidth = 614.295 - 2 * (72.27 + \oddsidemargin)
%
\setlength{\oddsidemargin}{13pt}
\setlength{\evensidemargin}{13pt}
\setlength{\textwidth}{443.0pt}

\begin{document}

%% Front matter
\title{Books Series in Astronomy and Astrophysics}
\author{James R. Fowler}
\date{last updated 28 July 2018\\ copy of \today}

%\begin{titlepage}
  \maketitle
%\end{titlepage}

\tableofcontents
\listoftables

%\begin{abstract}
%\end{abstract}

\section{Introduction}

In the tables below an asterisk by the book means that I have a copy.

Some of the books in \Cen{20} both popular as well as technical were published
as a series. Some questions we might ask are:

\begin{itemize}
  \item Why are series used by publishers and editors in general?
  \item How do these series fit into the bigger picture of book publishing?
  \item Why publish as a series in astronomy and astrophysics?
  \item What series exist in astronomy and astrophysics?
\end{itemize}

Read the editor's introduction, usually in the first volume, to
find the answers to the questions.
  
Of each series we can ask;

\begin{itemize}
  \item Is this a popular work or a professional volume?
  \item How well does it achieve this goal?
  \item How many copies of each printing were produced?
  \item How well did these copies sell?
\end{itemize}

\import{./}{HarvardBooksAstronomy}
\import{./}{uchicago}
\import{./}{uaspacescience}
\import{./}{asslKluwer}

\section{Other Series}

\begin{itemize}
  \item Annual Reviews of Astronomy and Astrophysics 1963 -- present *
  \item Vistas in Astronomy
  \item Astronomical Society of the Pacific Conference Series
  \item Astrophysics and Space Science Library from Reidel
  \item Astronomy and Astrophysics Library from Springer-Verlag, 100 volumes beginning in 1978, ISSN 0941-7834, \url{http://www.springer.com/us/astronomy/}
  \item Cambridge Astrophysics Series
  \item Interscience Tracts on Physics and Astronomy
  \item Princeton Series in Astrophysics
  \item Hutchinsons's Scientific and Technical Publications
  \item Topics in Astrophysics and Space Physics from Gordon and Breach. Check ISBN 0677142951
  \item Others?
\end{itemize}

\section{Additional Tables}

\import{./}{asslKluwer\_table}

\end{document}
