%% Begin copyright
%%
%%  /home/jrf/Documents/books/Books20/Docs/Series/springer.tx
%%
%%   Part of the Books20 Project
%%
%%   Copyright 2018 James R. Fowler
%%
%%   All rights reserved. No part of this publication may be
%%   reproduced, stored in a retrival system, or transmitted
%%   in any form or by any means, electronic, mechanical,
%%   photocopying, recording, or otherwise, without prior written
%%   permission of the author.
%%
%%
%% End copyright
\section{Springer-Verlag Publishing}

Following an apprenticeship of ten years to various bookseller, Julius
Springer (1817--1878) opened his own book store in Berlin in 1842. At
the same time he began publishing a small number of books and pamphlets
under the imprint {\it Verlag von Julius Springer}.  By 1858 however,
the publishing business had expanded greatly and he sold the book
shop. Although pursuing a number of different directions at times he
eventually came to prefer practical books (\cite{Sarkowski1996} p 80).
See also p129, v1p3.

Springer-Verlag in ????.The name was again changed in ????, this time
to Springer-Nature Publishing upon the acquision of Nature magazine??.
The company under what ever name had a strong interest in nature and
science and has developed many series in astronomy and astrophysics.

\subsection{Astrophysics and Space Science Library}

The series {\it Astrophysics and Space Science Library} was published
by Kluwer Academic from 1965-1999 and by Springer after 2000 following
their acquisition of Kluwer.  The ISSN number is 0067-0057. There are
some 440+ titles in the series as of 2018 and they are continuing to
be published.  It appears that most of the volumes are monographs but
some are workshop papers while others are historical. See Table
\ref{assl-springer:1} for the complete listing.

\subsection{Astronomy and Astrophysics Library}
  
The {\bf Astronomy and Astrophysics Library} was started in 1978 and
continues to the present. The ISSN number is 094-7834. The volumes are
listed in Table \ref{aal-springer:1}.
