%%
%%
%% uchicago.tex
%%
%%   Notes on the book series from the University of 
%%   Chicago .  This is information used
%%   with the book project "Some Important Books in Astronomy
%%    and Astrophysics in the 20th Century"
%%
%%   Copyright 2017 James R. Fowler
%%
%%   All rights reserved. No part of this publication may be
%%   reproduced, stored in a retrival system, or transmitted
%%   in any form or by any means, electronic, mechanical,
%%   photocopying, recording, or otherwise, without prior written
%%   permission of the author.
%%
%%
%%
\section{The Solar System}

Published by the University of Chicago the series consisted of four
volumes.  The general editor for the entire series was Gerald
P.\ Kuiper. Volumes one and two list two future volumes as \bt{Planets
  and Comets, part 1}, and \bt{Planets and Comets, part 2}.  However,
the third volume was published as \bt{Planets and Satellites}. It
listed the fourth volume as \bt{The Moon, Meteorites, and Comets}
which was the title of the fourth volume as published. Both the third
and fourth volumes list a planned fifth volume titled \bt{Planets,
  Interplanetary Medium}, but it was apparently never published. The
volumes were issued with pictoral dust jackets.  The series is
possibly the best summary of Solar System physics at the dawn of the
space age and planetary exploration.

\begin{longtable}{l l l}
  \caption{\bf University of Chicago \bt{Solar System} Series} \\
  \label{uocss:1} \\
  
  Title & Editor(s) & Date \\
  \hline\hline
  \endfirsthead
  
  \multicolumn{3}{c}{Continuation of Solar System Series} \\
  Title & Editor(s) & Date \\
  \hline\hline

  \endhead

  \hline
  \endfoot
  
  \hline\hline
  \endlastfoot

  \bt{The Sun} & Gerald P.\ Kuiper & 1953 \\
  & & 2 printing 1954 \\
  \bt{The Earth as a Planet} & Gerard P.\ Kuiper & 1954 * \\
  \bt{Planets and Satellites} & Gerard P.\ Kuiper & 1961 \\
  & Barbara M.\ Middlehurst & \\
  & & 3 printing 1971 \\
  \bt{The Moon, Meteorites and Comets} & Barbara M.\ Middlehurst & 1963 \\
  & Gerald P.\ Kuiper & \\
\end{longtable}


\section{Stars and Stellar Systems}

Published by the University of Chicago in the 1960's as an extension
to the \bt{Solar System} series. Its aim was ``to present stellar
astronomy and astrophysics as basically empirical sciences,
co-ordinated and illuminated by the application of theory.''
%\cite{kuiper:1961} page number
The general editors for the series were Gerard P.\ Kuiper and Barbara
M.\ Middlehurst with separate editors for each volume.  See table
\ref{uocsss:1} for publishing details.

\begin{longtable}[p]{l l l}
  \caption{\bf University of Chicago \bt{Stars and Stellar Systems} Series} \\
  \label{uocsss:1} \\
  
  Title & Editor(s) & Date \\
  \hline\hline
  \endfirsthead
  
  \multicolumn{3}{c}{Continuation of Stars and Stellar Systems} \\
  Title & Editor(s) & Date \\
  \hline\hline
  \endhead

  \hline
  \endfoot
  
  \hline\hline
  \endlastfoot

  \bt{Telescopes} & Gerald P. Kuiper & 1960 \\
  & Babara M.\ Middlehurst & \\

  \bt{Astronomical Techniques} & William A.\ Hiltner & 1962 \\
  & & fourth printing 1969 * \\

  \bt{Basic Astronomical Data} & K.\ Aa.\ Strand & 1963 \\
  & & third printing 1969 * \\

  \bt{Clusters and Binaries} & Harold Weaver & not published \footnotemark \\
   
  \bt{Galactic Structure} & Adrian Blaauw & 1965 \\
  & Maarten Schmidt & third printing 1975 * \\

  \bt{Stellar Atmospheres} & & \\

  \bt{Nebulae and Interstellar Matter} & Barbara M.\ Middlehurst & 1968 * \\
  & Lawrence H.\ Aller & \\

  \bt{Stellar Structure} & Lawrence H.\ Aller & 1965 * \\
  & Dean B. McLaughlin & \\

  \bt{Galaxies and the Universe} & Allan Sandage & 1975 \\
  & Jerome Kristian & \\
  
\end{longtable}

\footnotetext{See \url{https://www.cloudynights.com/topic/406687-help-me-find-stars-and-stellar-systems-vol-4/} (last accessed 2018-07-28) for information about Volume 4.}
