%%
%%
%% Notes.bib
%%
%%   Notes on the books and articles that have been read in conjunction
%%   with the book project "Some Important Books in Astronomy
%%    and Astrophysics in the 20th Century"
%%
%%   Copyright 2009 James R. Fowler
%%
%%   All rights reserved. No part of this publication may be
%%   reproduced, stored in a retrival system, or transmitted
%%   in any form or by any means, electronic, mechanical,
%%   photocopying, recording, or otherwise, without prior written
%%   permission of the author.
%%
%%
%% The last known changes were checked in by $Author$
%% as revision $LastChangedRevision$
%% on $Date$
%%
%%

%% 

\documentclass{article}

\usepackage{books20}
\addglobalbib{./../../Docs/MasterBib.bib}

\begin{document}

%%\frontmatter
\title{Some Notes on Books Read}
\author{James R. Fowler}
\date{copy of \today}
\maketitle

\section{Notes on Notes}

{\bf 10/19/2010} Format for Note Taking

Still can't quite make up my mind on how I want to take
notes. Handwritten notes on paper has been my medium of choice for 30
years now. However, since any writing I do will be on the computer
electronics notes are advantageous.  So paper notes that I might take
at times when my computer is not available will be transcribed into
electronic form. This will be a nuisance as it means writing notes
twice but it also means that notes are readable five years later.
When a computer is available notes will be written directly to
electronic form and if necessary, copied into this document.  By using
\TeX\ the notes can be formatted neatly although one has a lot more
flexibility with handwritten notes. On the other hand, with electronic
notes I can change my mind about the note during the composition.
Indeed, I changed by mind about the rules portion of this note; at
first is was to be a paragraph but I quickly realized that it would be
more readable as a list.

I need to consolidate the note taking in some preferred format.  Right now
I have paper notes as well as electronic notes on multiple computer
and in multiple formats.

My rules for taking notes:
\begin{itemize}
\item {\bf Always} include a date for the note. Put the date in bold face.
\item If a note is about a book or from a book, include the title,
  author and a citation from the master bibliography as well as
  chapter and page reference. The master bibliography should include
  Library of Congress and Dewey Decimal catalog numbers.
\item Never change an electronic note after it has been written. This
  includes misspellings. Changes may be made while composing notes but
  not the next day. Instead make a dated addition to the note. We wish
  to preserve the historical flow and avoid any {\it 1984} style of
  rewriting history.
\item Keep a paper copy. Scribble on it as necessary. Update this file.
The paper copy of this file should aways include the date that it was
processed from \TeX\ to PDF.
\end{itemize}

Some references that I have used for trying to find the best way to take
notes.
\begin{itemize}
\item My thirty years of reading and note taking mostly with pen and  paper.
\item Booth, W., et al.\ {\it The Craft of Research 3rd. ed.}
  \cite{booth:2008}
\item Cronon, William, {\it Learning to Do Historical Research}
  http://williamcronon.net/researching/index.htm specifically the
  section on note taking
  http://williamcronon.net/researching/notetaking.htm
  \cite{cronon:2008}
\item Cantor and Schnieder, {\it How to Study History} \cite{cantor:1967}
\end{itemize}


%%\mainmatter

\section{Notes about the History of Astronomy}\
\input{18Cent}

\section{Note about Books}\
\input{book_notes}

\section{Notes about Bibliographies}\
\input{biblio_notes}

\section{Notes about \ensuremath{19^{th}} and \ensuremath{20^{th}} Century World History}\
\input{world_history_notes}

%\section{History of Reading}\
%\input{hist_reading_notes}

\section{Notes on the Sociology of Science}\
\input{socsci_notes}

\section{History and Historiography}\
\input{history_notes}

%%\backmatter
\vfil\eject

\printbibliography

\end{document}
